Combination of generic and specific layers in multidomain learning

### 2020-09-02 2020/tacl2020/rebuttal.tex

  We have tried to address these commentaries in the revised version of the paper. Notably, we have clarified the distinction between \system{FT-block} and \system{MDL Res} (see details below). We have also tried to clarify the distinction between multi-domain MT and fine-tuning; while the former is designed with an a priori knowledge that the test data is sampled from a single domain, the latter assumes that the test data will be sampled from multiple domains, using domain probabilities that are not known a priori. This raises the issues of robustness wrt to adversarial test distribution and even new domains, two issues that are somewhat irrelevant for DA.
\\
In our experiments, fine-tuned systems share no parameter and show large drops in performance when translating data from the wrong domain (even though this could be somewhat mitigated through regularization, as the reviewer points out). By contrast, the majority of the parameters of our MDMT systems are shared for all domains. Arguably, one could see here a continuum between no parameter sharing and full parameter sharing, with \system{MDL Res} and \system{FT Block} corresponding to some intermediay situation. 
}
\noindent Question to authors:
\item can you describe in more detail the differences between \system{FT-Block} and \system{MDL Res}, apart from the fact that the former is fine-tuned from a generic model, the latter trained from scratch~?
    The two methods use the same architecture composed of one standard Transformer model extended with domain adapters following the design of \cite{Bapna19simple}. As the reviewer correctly points out, the only difference between \system{FT-block} and \system{MDL Res} is their training process and training data distribution.
    To train \system{FT-block}, we plug residual adapters to the output of each self-attention layer of the generic model Mixed-NAT, then resume the training with the learning rate attained at the end of the training the generic model while freezing all of the other parameters of the model \system{Mixed-NAT}. For this step, we only use only the in-domain data, as we do during the full-tuning procedure.
    To train MDL res, we optimize the parameters of the Transformer model and the parameters of the residual adapters from scratch. More precisely, to create a training batch, we randomly pick a domain with a probability equal to the proportion of the domain in training data, then sample a batch from the corresponding corpus. Given a batch from domain $i$, we simultaneously optimize the parameters of Transformer model and the parameters of the residual adapters for that domain.
    We understand that our naming schemes was insisting on training procedures, rather than on architectures, thus possibly introducing some confusions. We have accordingly changed the name of \system{FT-Block} to \system{FT Res}, clarified the description of the two systems (see lines YYY\fyTodo{fix this}), and reported \system{FT Res}\fyTodo{or new name} as another multi-domain system in all tables.\fyTodo{Make sure it is the case}.}
  %}

### 2020-09-02 2020/wada/adaptive_domain_adaptation.tex

 A ``gated'' version uses $h' = h + a_k(h) \odot{} z_k(h)$\footnote{Or $a_k(h) = \sum_{l} a_{kl}(h)$, where the summation runs over layers, see Figure~\ref{fig:architecture}} \fyDone{$a_k(h)=$ somme tous les composants résiduels} where $z_k$ is a function of $h$ taking values in $[0,1]$. More precisely, $h$ and $h'$ are sequences of context vectors and the combination is performed element-wise, yielding:\fyDone{pourquoi pas gating: $(1-a_k(h(w))*hh(w)$ ? Notation mult. component wise ?}

@@

  Domain classifiers take as input the output of the encoder and the output of the decoder, i.e at the last self-attention layer of the encoder and the attention layer of the decoder. \fyDone{Next sentence is a repetition}
  % Two classifiers are placed respectively on top of the last encoder and decoder layers:
  \begin{align}
    \forall t \in [1 \dots T], h_{enc}(w^{src}_t) = Enc(x)(w^{src}_t), z^{enc}_k(w^{src}_t) = p(k| h^{enc}(w^{src}_t))
  \end{align}
  \fyTodo{what are x and y ?}
  and
  \begin{align}
    h_{dec}(w^{tgt}_t)=Dec(x, y_{i<t})(w^{tgt}_t)  z^{dec}_k(w^{tgt}_t) = p(d=k| h_{dec}(w^{tgt}_t))
  \end{align}

@@

Furthermore $ \varepsilon^k_{insep} < \varepsilon_{insep} $ which is the minimum of the error expectation over the hypothesis space of the classifier. With a trivial prediction $[\frac{1}{K},..,\frac{1}{K}]$ we have an error expectation equal to $0.5$. Therefore, $\varepsilon_{insep} \leq 0.5$, i.e, $\varepsilon_{insep}(k) < 0.5$.\fyTodo{Je ne comprends pas.} In the worst case where domains in the mixture are very close, we are still able to reduce the risk of predicting out-of-domain examples by a factor of 2.
\fyTodo{I sort of buy the equations but then so what ? We should may be compare with non-adaptive ?}

>>>>

 A ``gated'' version uses $h' = h + a_k(h) \odot{} z_k(h)$\footnote{Or $a_k(h) = \sum_{l} a_{kl}(h)$, where the summation runs over layers, see Figure~\ref{fig:hrl-architecture}} \fyDone{$a_k(h)=$ somme tous les composants résiduels} where $z_k$ is a function of $h$ taking values in $[0,1]$. More precisely, $h$ and $h'$ are sequences of context vectors and the combination is performed element-wise, yielding:\fyDone{pourquoi pas gating: $(1-a_k(h(w))*hh(w)$ ? Notation mult. component wise ?}

@@

  Domain classifiers take as input the output of the encoder and the output of the decoder, i.e at the last self-attention layer of the encoder and the attention layer of the decoder. \fyDone{Next sentence is a repetition}
  % Two classifiers are placed respectively on top of the last encoder and decoder layers:
  \begin{align}
    \forall t \in [1 \dots T], h_{enc}(w^{src}_t) = Enc(x)(w^{src}_t), z^{enc}_k(w^{src}_t) = p(k| h^{enc}(w^{src}_t))
  \end{align}
  \fyTodo{what are x and y ?}
  and
  \begin{align}
    h_{dec}(w^{tgt}_t)=Dec(x, y_{i<t})(w^{tgt}_t)  z^{dec}_k(w^{tgt}_t) = p(d=k| h_{dec}(w^{tgt}_t))
  \end{align}
  Where x is source sentence, y is target sentence, $x=\lbrace w^{src}_0,..,w^{src}_{T_0}\rbrace$, $y=\lbrace w^{tgt}_0,..,w^{tgt}_{T_1} \rbrace$

@@
